COVID-19 Policy-Compliance in Europe

### 2020-12-24 Draft.Rmd
Automated Regression table output in html

THE FOLLOWING MUST BE UPDATED

@@

@@

>>>>

@@

```{r Regression Table, echo=FALSE, results="asis", fig.align='center'}

# Fit the model
lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)

# Generate regression table
texreg::htmlreg(lm1, single.row = TRUE, 
#                         custom.header = list("Model Results" = 1),
#                         model.names = c("My name 1", "My name 2"), 
                         custom.coef.names = c("Intercept", "Date", "Publicity",
                                               "Cases/100,000/14 Days",
                                               "Belgium",
                                               "Denmark",
                                               "France",
                                               "Germany",
                                               "Ireland",
                                               "Italy",
                                               "Netherlands",
                                               "Poland",
                                               "Spain",
                                               "Sweden",
                                               "United Kingdom"),
                          bold = 0.05,
                          center = TRUE,
                          caption = "Regression Table"
                         )
```

@@

THIS TABLE WILL BE UPDATED BEFORE FINAL SUBMISSION
